Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-07 paper.tex
Address specific comments on Pages 10-12

The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak $N^2$ maximum just above the cold-point tropopause.
Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased within the 25-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
Outside of the eye, meanwhile, the tropopause height decreased over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
In this outer region, the $N^2$ maximum just above the tropopause strengthened during RI.
These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
The mechanisms that led to these $N^2$ changes will be investigated in the subsequent sections.

@@

\paragraph{0-24 hours}\mbox{}\\
\indent The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
At and immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary driver of the $N^2$ tendency during this period, acting to stabilize near and just below the tropopause and destabilize above.
Although vertical turbulence acted in opposition to advection (i.e. it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above the tropopause.
Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.

\paragraph{24-48 hours}\mbox{}\\
\indent During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.

>>>>

The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak $N^2$ maximum just above the cold-point tropopause.
Over the subsequent 24 hours, during the RI period, the $N^2$ within and above this layer decreased within the 25-km radius (Fig.~\ref{fig:n2-24hr-avgs}b).
This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximized at the storm center.
Outside of the eye, meanwhile, the tropopause height decreased over the eyewall region (25-60-km radius) and increased only slightly outside of the 60-km radius.
In this outer region, the $N^2$ maximum just above the tropopause strengthened during RI.
These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
Static stability outside of the eye, meanwhile, continued to increase just above the cold-point tropopause.
This $N^2$ evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}, see their Fig. 4).
The mechanisms that led to these $N^2$ changes will be investigated in the subsequent sections.

@@

\paragraph{0-24 hours}\mbox{}\\
\indent The initial spin-up period was characterized by a steady increase of the maximum wind speed from 11 m s\textsuperscript{-1} to 22 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}a, blue line), an intensification rate that closely matched that of TC Patricia (Fig.~\ref{fig:vmax+pmin}a, red stars).
The weakening of the lower-stratospheric $N^2$ maximum during this period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
At and immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary driver of the $N^2$ tendency during this period, acting to stabilize near and just below the tropopause and destabilize above.
Although vertical turbulence acted in opposition to advection (i.e. it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above the tropopause.
Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduced the total change in $N^2$ almost exactly.

\paragraph{24-48 hours}\mbox{}\\
\indent During the RI period, the maximum wind speed increased from 22 m s\textsuperscript{-1} to 80 m s\textsuperscript{-1}.
Over this time, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b).
Vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.
